---
title: "HW_02"
author: "MINSI SUNG"
date: "21/09/2019"
output: 
  html_document:
    keep_md: true
editor_options: 
  chunk_output_type: inline
---

<!---The following chunk allows errors when knitting--->

```{r allow errors, echo = FALSE}
knitr::opts_chunk$set(error = TRUE)
```
    
```{r load packages, warning = FALSE, message = FALSE}
# load your packages here:
library(gapminder)
library(tidyverse)
```
    

## Exercise 1: Basic dplyr
*Use dplyr functions to achieve the following.*

### 1.1 Use filter() to subset the gapminder data to three countries of your choice in the 1970’s.
Here I chose Japan, Taiwan and China these three countries
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  filter(year >= 1970 | year<1979) %>% 
  filter(country == 'Japan' | country == 'Taiwan' | country == 'Germany')
```
### 1.2 Use the pipe operator %>% to select “country” and “gdpPercap” from your filtered dataset in 1.1.
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
    filter(year >= 1970 | year<1979) %>% 
      filter(country == 'Japan' | country == 'Taiwan' | country == 'Germany') %>% 
        select(country,gdpPercap)
```
### 1.3 Filter gapminder to all entries that have experienced a drop in life expectancy. Be sure to include a new variable that’s the increase in life expectancy in your tibble. Hint: you might find the lag() or diff() functions useful.
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  group_by(country) %>% 
  arrange(year) %>% 
  mutate(difference = lifeExp - lag(lifeExp,1)) %>% 
  filter(difference<0)
```
### 1.4 Filter gapminder so that it shows the max GDP per capita experienced by each country.
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  group_by(country) %>% 
  summarize(max_gdpPercap = max(gdpPercap))
```


### 1.5 Produce a scatterplot of Canada’s life expectancy vs. GDP per capita using ggplot2, without defining a new variable. That is, after filtering the gapminder data set, pipe it directly into the ggplot() function. Ensure GDP per capita is on a log scale.
```{r, warning=FALSE, echo=FALSE}
ggplot(gapminder %>% 
         filter(country == 'Canada'), aes(lifeExp, gdpPercap)) +
  geom_point()
```


## Exercise 2:Explore individual variables with dplyr
Pick one categorical variable and one quantitative variable to explore. Answer the following questions in whichever way you think is appropriate, using dplyr:

The categorical variable I picked is `Continent`
The quantitative variable I would like to explore is `gdpPercap`



* What are possible values (or range, whichever is appropriate) of each variable?

The possible varlues of the categorical `continent` is:
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  select(continent) %>% 
  distinct(continent)
```

The range of the quantitive variable `gdpPercap` is:

```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
select(gdpPercap) %>% 
range()
```
From 241.1659 to 113523.1329 is the range of gdpPercap


* What values are typical? What’s the spread? What’s the distribution? Etc., tailored to the variable at hand.


```



* Feel free to use summary stats, tables, figures.




## Exercise 3: Explore various plot types 
Make two plots that have some value to them. That is, plots that someone might actually consider making for an analysis. Just don’t make the same plots we made in class – feel free to use a data set from the datasets R package if you wish.

1. A scatterplot of two quantitative variables.
```{r}
ggplot(gapminder %>% 
         filter(country == 'Taiwan'), aes(lifeExp, pop)) +
  geom_point()
```

2. One other plot besides a scatterplot.


## Recycling (Optional) (extra 2%)
For people who want to take things further.

Evaluate this code and describe the result. Presumably the analyst’s intent was to get the data for Rwanda and Afghanistan. Did they succeed? Why or why not? If not, what is the correct way to do this?

`filter(gapminder, country == c("Rwanda", "Afghanistan"))`



## Tibble display (Optional) (extra 1%)
Present numerical tables in a more attractive form using `knitr::kable()` for small tibbles (say, up to 10 rows), and `DT::datatable()` for larger tibbles.
