---
title: "HW_02"
author: "MINSI SUNG"
date: "21/09/2019"
output:
  html_document:
    keep_md: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---
    
    
```{r load, warning=FALSE,echo=FALSE}
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(tidyverse))  # included package 'dplyr'
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(knitr))  # tidy tables
suppressPackageStartupMessages(library(DT))  # tidy dataframe tables for HTML
```
    

# Exercise 1: Basic dplyr
*Use dplyr functions to achieve the following.*

### 1.1 Use filter() to subset the gapminder data to three countries of your choice in the 1970’s.
Here I chose Japan, Taiwan and China these three countries
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  filter(year >= 1970 & year<1979) %>% 
  filter(country == 'Japan' | country == 'Taiwan' | country == 'Germany')
```
### 1.2 Use the pipe operator %>% to select “country” and “gdpPercap” from your filtered dataset in 1.1.
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
    filter(year >= 1970 | year<1979) %>% 
      filter(country == 'Japan' | country == 'Taiwan' | country == 'Germany') %>% 
        select(country,gdpPercap)
```
### 1.3 Filter gapminder to all entries that have experienced a drop in life expectancy. Be sure to include a new variable that’s the increase in life expectancy in your tibble. Hint: you might find the lag() or diff() functions useful.
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  group_by(country) %>% 
  arrange(year) %>% 
  mutate(difference = lifeExp - lag(lifeExp,1)) %>% 
  filter(difference<0)
```
### 1.4 Filter gapminder so that it shows the max GDP per capita experienced by each country.
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  group_by(country) %>% 
  summarize(max_gdpPercap = max(gdpPercap))
```


### 1.5 Produce a scatterplot of Canada’s life expectancy vs. GDP per capita using ggplot2, without defining a new variable. That is, after filtering the gapminder data set, pipe it directly into the ggplot() function. Ensure GDP per capita is on a log scale.
```{r, warning=FALSE, echo=FALSE}
ggplot(gapminder %>% 
         filter(country == 'Canada'), aes(lifeExp, gdpPercap)) +
  scale_y_log10("GDP per capita", labels = scales::dollar_format())+
  geom_point()+
  labs(x="Life Expectancy", y="GDP per capita (Log)")
```


# Exercise 2:Explore individual variables with dplyr
Pick one categorical variable and one quantitative variable to explore. Answer the following questions in whichever way you think is appropriate, using dplyr:

The categorical variable I picked is `Continent`
The quantitative variable I would like to explore is `gdpPercap`



###  What are possible values (or range, whichever is appropriate) of each variable?

The possible varlues of the categorical `continent` is:
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  select(continent) %>% 
  distinct(continent)
```


### What values are typical? What’s the spread? What’s the distribution? Etc., tailored to the variable at hand.

```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  group_by(continent) %>% #This tells you the possible values for continent
 summarize(min(gdpPercap) # The minimum gdpPercap by each continent
           ,max(gdpPercap) # The maximum  (max - min = range)
           ,mean(gdpPercap) #The mean gdpPercap which means typical
           ,sd(gdpPercap)) #The standard deviation of the gdpPercap which can be a measure of spread

```


The distribution of the gdpPercap of each continent
```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  ggplot(aes(x=log(gdpPercap)))+ 
  geom_density()+ #Plot density
    facet_wrap(~continent) #plot the density side by side
```


# Exercise 3: Explore various plot types 
Make two plots that have some value to them. That is, plots that someone might actually consider making for an analysis. Just don’t make the same plots we made in class – feel free to use a data set from the datasets R package if you wish.

### 1. A scatterplot of two quantitative variables.

```{r, warning=FALSE, echo=FALSE}
gapminder %>%
  filter(country=='Taiwan') %>% 
  ggplot(aes(x=lifeExp, y=gdpPercap)) +
    geom_point(aes(colour = pop),size = 5) +
      geom_text(aes(label=year), nudge_x = -1.2) +
        labs(title="A Scatterplot on GDP and Life Expectancy of Taiwan", 
             x="Life Expectancy", y="GDP per capita")
```

### 2. One other plot besides a scatterplot.

```{r, warning=FALSE, echo=FALSE}
gapminder %>% 
  filter(country=='Taiwan' | country=='China' | country=='Japan'| country=='Canada') %>% 
  ggplot(aes(x=year, y=lifeExp, col=country)) +
    geom_line() +
      labs(title='A Lineplot on Life Expectancy Changes for four countries ', 
           x='Country', y='Life Expectancy')

```

## Recycling (Optional) (extra 2%)
For people who want to take things further.

Evaluate this code and describe the result. Presumably the analyst’s intent was to get the data for Rwanda and Afghanistan. Did they succeed? Why or why not? If not, what is the correct way to do this?

```{r}

filter(gapminder, country == c("Rwanda", "Afghanistan"))

```

```{r}
gapminder %>% 
filter(country == "Rwanda" |country ==  "Afghanistan")

```

From the comparison above we can see that they did NOT succeed to get all the data of Rwanda and Afghanistan. It's because first one only list out the data which 'country == c("Rwanda", "Afghanistan")'. The correct one lists out all the data which country equal to Rwanda or Afghanistan.

## Tibble display (Optional) (extra 1%)
Present numerical tables in a more attractive form using `knitr::kable()` for small tibbles (say, up to 10 rows),

```{r }
gapminder %>%
  filter(country == "Rwanda" |country ==  "Afghanistan") %>% 
  top_n(10) %>% 
  knitr::kable()
```

and `DT::datatable()` for larger tibbles.

```{r }
gapminder %>%
  filter(country == "Rwanda" |country ==  "Afghanistan") %>% 
  DT::datatable()
```

