---
title: "HW01_gapminder"
author: "MINSI SUNG"
date: "12/09/2019"
output: 
  html_document:
    keep md: true
    toc: true
    number_sections: true
    toc_float: false
---



```{r load, warning=FALSE, echo=FALSE}
library(gapminder)
library(tibble)
library(DT)
library(ggplot2)
```

# Explore gapminder 

Let's load the dataset `gapminder` which is available in R. 

### Summary statistics for the dataset:
```{r summary, warning=FALSE, echo=FALSE}
summary(gapminder)
```
The dataset contains ``r nrow(gapminder)`` rows and ``r ncol(gapminder)`` columns.


All the variables we have:
```{r names , warning=FALSE, echo=FALSE}
names(gapminder)
```
The number of countries in the dataset is ``r length(unique(gapminder$country))``.
The number of years in the dataset is ``r length(unique(gapminder$year))``


This is the mean life expectancy over all countries for all years:
```{r, warning=FALSE, echo=FALSE}
mean(gapminder$lifeExp, na.rm=T)
```


# Asia

Now let's check the `gapminder` data for Asia.
```{r , warning=FALSE, echo=FALSE}
plot(gapminder$year[gapminder$continent=="Asia"], gapminder$lifeExp[gapminder$continent=="Asia"], ylab = "life expectancy", xlab = "Year", main="Life expectancy in Asia by year")
```

### Summary statistics for Asia:

* population:
```{r , warning=FALSE, echo=FALSE}
summary(gapminder$pop[gapminder$continent=="Asia"])
```
* life expectancy:
```{r , warning=FALSE, echo=FALSE}
summary(gapminder$lifeExp[gapminder$continent=="Asia"])
```

* GDP per capita:
```{r , warning=FALSE, echo=FALSE}
summary(gapminder$gdpPercap[gapminder$continent=="Asia"])
```