---
title: "HW01 gapminder Presentation"
author: "MINSI SUNG"
date: "12/09/2019"
output: 
  ioslides_presentation:
   keep_md: true
---



```{r load, warning=FALSE, echo=FALSE}
library(gapminder)
library(tibble)
library(DT)
library(ggplot2)
```

# Explore gapminder 

## Summary statistics for the dataset:
```{r summary, warning=FALSE, echo=FALSE}
summary(gapminder)
```
## The dataset contains 
### ``r nrow(gapminder)`` rows and ``r ncol(gapminder)`` columns.


### All the variables we have:
### ``r names(gapminder)[1:3]`` rows and ``r names(gapminder)[4:6]``


### The number of countries in the dataset is ``r length(unique(gapminder$country))``.
### The number of years in the dataset is ``r length(unique(gapminder$year))``


## 
### The mean life expectancy over all countries for all years is ``r mean(gapminder$lifeExp, na.rm=T)``.


## Asia

### Now let's check the `gapminder` data for Asia.
```{r , warning=FALSE, echo=FALSE}
plot(gapminder$year[gapminder$continent=="Asia"], gapminder$lifeExp[gapminder$continent=="Asia"], ylab = "life expectancy", xlab = "Year", main="Life expectancy in Asia by year")
```

## Summary statistics for Asia:

* population:
```{r , warning=FALSE, echo=FALSE}
summary(gapminder$pop[gapminder$continent=="Asia"])
```
* life expectancy:
```{r , warning=FALSE, echo=FALSE}
summary(gapminder$lifeExp[gapminder$continent=="Asia"])
```

* GDP per capita:
```{r , warning=FALSE, echo=FALSE}
summary(gapminder$gdpPercap[gapminder$continent=="Asia"])
```

