---
title: "HW_03"
author: "MINSI SUNG"
date: "26/09/2019"
output:
    html_document:
    keep_md: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r , warning=FALSE,echo=FALSE}
suppressPackageStartupMessages(library(tidyverse)) 
suppressPackageStartupMessages(library(gapminder))
suppressPackageStartupMessages(library(knitr))
```

# Task Option 2
### Get the maximum and minimum of GDP per capita for all continents.
```{r}
gapminder %>% 
  group_by(continent) %>% 
summarize(max_gdpPercap = max(gdpPercap), min_gdpPercap = min(gdpPercap))%>% 
  knitr::kable()
```


# Task Option 3
### Look at the spread of GDP per capita within the continents.
```{r}
  ggplot(gapminder, aes(continent, gdpPercap,color = continent)) +
  geom_point(alpha = 0.1) +
  scale_y_log10(labels = scales::comma_format())

```


# Task Option 5
### How is life expectancy changing over time on different continents?

Since there are lots of lifeExp data in each continent, we need to get the mean of the lifeExp for each continent and plot its changing over time.

```{r}
gapminder %>% 
  group_by(year, continent) %>% 
  summarize(mean_lifeExp = mean(lifeExp)) %>% 
  ggplot(aes(year, mean_lifeExp, group = continent, colour = continent)) +
  geom_line()
```

